---
title: "Final Presentations"
format: 
  html:
    toc: true
    code-line-numbers: true
editor_options: 
  chunk_output_type: console
---


```{r}
#| echo: false

exercise_number <- 1

```

## Complete course evaluations

The graduate programs asked that professors reserve time at the start of class for students to fill out their course evaluations. I will give everyone 10 minutes (5 minute check-in) to fill out the course evaluation.

## Final presentations

The goal of this final is to develop and deliver a clear, concise, and engaging presentation on a topic of your choice within a strict 5-minute time limit, but your target audience will be randomized. This exercise will help you improve your research, organization, and public speaking skills.

The presentation topic can be anything you learned in this course. It can be on something you wrote, in class discussion, contents in the book or other materials you read/watched, as long as it relates back to security, privacy, ethics, and equity.

### Target audience and presentation topic

Student Last Name | Target Audience | Presentation Topic
----- | ----- | -----   
Androlewicz | family-friends | 
Boyar | family-friends | 
Choate | family-friends | Geopolitical impacts and privacy risks of transmitting individual US data across borders
Clayman | family-friends | 	
Cousins | classmates-coworkers | 
Daversa | local-government-policymaker | Importance of GIS data for decision-making and the security aspects of collecting better GIS data 
Dowdy | classmates-coworkers | 
Duhil de Benaze | classmates-coworkers| How human behaviors, such as phishing, weak passwords, and social engineering create vulnerabilities in cybersecurity systems
Espinal-Guzman | family-friends | 	
Gallishaw | local-government-policymaker | Recent work on creating a national privacy law, such as the American Data Privacy and Protection Act proposal and/or the American Privacy Rights Act proposal
Garratt | funders-media | Protecting relationship data 
Kim | local-government-policymaker | Privacy and ethical concerns for children on social media
Morris | funders-media  | Ethics of AI in sports
Mueller | local-government-policymaker | Environmental issues, water quality data
O’Brien | family-friends |
OKeefe | family-friends| Football and concussion injuries and ramifications
Pacheco | classmates-coworkers | Normalization of surveillance in digital and physical spaces and the ethical concerns
Pushard | local-government-policymaker | 	
Scott | classmates-coworkers | Period tracking apps like Flo and how they use health data
Thadeio | classmates-coworkers | Security challenges in journalism through the lens of public media data 
Thorbahn | funders-media | Are phones actually listening to you?
Washington | funders-media | 


\* == indicates students swapped target audience.

### Evaluation of the presentation

TThe following is how I will evaluate your presentations. Each part will be scored from 1 to 6, as detailed below.

1. Content and audience (6 points)

   - 6: Clear purpose and content that addresses the target audience.
   - 3: Moderate clarity and relevance to the target audience.
   - 1: Unclear purpose and irrelevant to the target audience.

2. Organization and structure (6 points)

   - 6: Well-organized with a clear and strong flow (introduction, middle, and conclusion).
   - 3: Moderately organized with adequate flow.
   - 1: Poorly organized, missing key structural elements.

3. Delivery and timing (6 points)

   - 6: Enthusiastic and engaging, with good pacing, within 30 seconds of the time limit.
   - 3: Some enthusiasm and minor pacing issues, within 30 seconds to 1 minute of the time limit.
   - 1: Lacks enthusiasm, poor pacing, over 1 minute off the time limit.

4. Quality of slides or other visual aids (6 points)

   - 6: Enhances the presentation.
   - 3: Somewhat contributes to the presentation.
   - 1: Does not contribute to the presentation.

5. Overall quality (6 points)

   - 6: Highly effective in achieving the goal.
   - 3: Somewhat effective in achieving the goal.
   - 1: Ineffective in achieving the goal.

### Presentation order

```{r}
#| warning: false

set.seed(42)

library(tidyverse)
library(dplyr)

sample(c("Androlewicz", "Boyar", "Choate", "Clayman", "Cousins", "Daversa", 
              "Dowdy", "Duhil de Benaze", "Espinal-Guzman", "Gallishaw", "Garratt", "Kim",
              "Morris", "Mueller", "O’Brien", "OKeefe", "Pacheoco",
              "Pushard", "Scott", "Thadeio", "Thorbahn", "Washington"), replace = FALSE)

```

### Schedule

Time (EDT) | Student Order
----- | ----- 
4:05 pm - 5:15 pm | Pacheoco
-- | Cousins
-- | Androlewicz
-- | Gallishaw
-- | Clayman
-- | Washington
-- | OKeefe
-- | O’Brien
-- | Duhil de Benaze
-- | Dowdy
-- | Pushard
**5:15 pm - 5:20 pm** | **Break**
5:20 pm - 6:30 pm | Espinal-Guzman
-- | Thorbahn
-- | Kim
-- | Boyar
-- | Mueller
-- | Choate
-- | Thadeio
-- | Scott
-- | Daversa
-- | Morris
-- | Garratt

### Vote for your favorite presentation

Each year, I ask students to vote for their favorite presentation. The person with the most votes will receive a gift card to a local café or restaurant of their choice (or whatever business as long as is locally owned), paid for by me. You cannot vote for yourself.

After all the presentations are complete, please submit your vote [here](https://forms.gle/7mdkCVFxG9eDTaEL8).